Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-08 Thesis/chapter/04-experimental.tex
drueber lesen bis excl 04 characterization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\td{COMMENT: solution age was not accounted for}
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squwares fo the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aquatic solution}\label{sec:exp-sol-aq}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous solutions. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Buthanolic solution}\label{sec:exp-sol-bu}
Five different concentrations of the buthanolic solutions were prepared. 
The \gls{1f} was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
Not all chemicals mentioned in \cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilisation compound (\gls{acoh}) was changed to \gls{ipo}.
The most promissing combination of solvent, chelating agent and stabilisation reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, which was used for the final optimisation.
The main differences between the used recipe and mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Most steel substrates (all pre-optimisation and optimisation samples) 
All steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
The rest was doctor bladed on a glass plate, fixed with double sided adhesive tape and 
partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.02}{\milli\meter} was used.
The heatable vacuum plate 
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep substrate in place (see 
figure~\ref{fig:eric}). Most of them were covered with tape to increase the suction at the remaining ones. After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the vacuum plate temperature (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}) were set, 
the blade was put into position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimisation samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution on the plate 
was removed with a 
wipe. The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (1) on the left,
		vacuum pump (2) in the background and 
		Erichsen Coatmaster 510 film applicator (3) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calcination}\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft} \gls{ir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aquatic solution}\label{sec:exp-sol-aq}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous layers. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Buthanolic solution}\label{sec:exp-sol-bu}
Five different concentrations of the buthanolic solutions were prepared. 
The \gls{1f} was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
Not all chemicals mentioned in \cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilisation compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilisation reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimisation.
The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Most steel substrates (all pre-optimisation and optimisation samples) 
All steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
%
Eventually, a heatable vacuum plate was used. It 
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep the substrate in place (see 
figure~\ref{fig:eric}). 
Most of them were covered with tape to increase the suction at the remaining ones. 
After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the vacuum plate temperature (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its original position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimisation samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (1) on the left,
		vacuum pump (2) in the background and 
		Erichsen Coatmaster 510 film applicator (3) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calcination}\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This heating procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft}\gls{uv}\gls{vis}\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

### 2022-11-08 Thesis/chapter/05-computational-details.tex
drueber lesen bis excl 04 characterization

\subsection{Sample Selection}
\label{sec:ss}
An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
Multivariate Adaptive Regression Splines (MARS) model\cite{Villanova2010,Kennedy1995,Breiman1997,Carta2011}.
%
"PSO is a population based heuristic inspired by the flocking behavior of birds. 
To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{Villanova2010}
%
Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline
		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
	\label{tab:input}
\end{table}

>>>>

\subsection{Sample Selection}
\label{sec:ss}
An evolutionary approach was chosen, namely a multi-objective Particle Swarm Optimization (PSO) with a multi-response
Multivariate Adaptive Regression Splines (MARS) model\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
"PSO is a population based heuristic inspired by the flocking behavior of birds. 
To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline
		Zr(PrO)$_4$ conc. [21 g/L]	&layers	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter \td{are concentrations correct?}}
	\label{tab:input}
\end{table}

### 2022-11-08 Thesis/chapter/063-discussion.tex
good draft results materials/pre-opt
drueber lesen bis excl 04 characterization

@@

>>>>

\td{"An important concept in inferential statistics is that the amount of information you can learn about a population is limited by the sample size. The more you want to learn, the larger your sample size must be." - by \url{https://blog.minitab.com/en/adventures-in-statistics-2/the-danger-of-overfitting-regression-models} } 
\td{"overfitting a regression model occurs when you attempt to estimate too many parameters from a sample that is too small." - same source}
\td{"However, if the effect size is small or there is high multicollinearity, you may need more observations per term." -same source}

@@

\td{what are the reasons for large error?} 
\begin{itemize} 
    \item ageing of solution 
    \item varying humidity
    \item varying room temperature 
    \item impurities in solutions
    \item inhomogeneity of film 
    \item measuring error
    \item 
\end{itemize}

What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.

\href{https://pubs.acs.org/doi/10.1021/ci0342472}{overfitting}
\td{COMMENT: solution age was not accounted for}
